%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Friggeri Resume/CV
% XeLaTeX Template
% Version 1.0 (5/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX and the bibliography, if used,
% needs to be compiled with biber rather than bibtex.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{friggeri-cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing


\begin{document}

\header{adam}{eliot}{computer scientist} % Your name and current job title/field

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{contact}
643 Braeside Cres
Kingston, Ontario 
K7P 1G6
Canada
~
+1 (226) 989 2779
~
\href{mailto:adameliot@gmail.com}{adameliot@gmail.com}
\href{mailto:aeliot@uwaterloo.ca}{aeliot@uwaterloo.ca}
\href{http://adam.eliot.ca}{http://adam.eliot.ca}
\section{programming}
C, C++, Python
Linux
\end{aside}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{education}

\begin{entrylist}
%------------------------------------------------
\entry
{2011--Current}
{Bachelor {\normalfont of Computer Science}}
{University of Waterloo}
{}

\entry
{2010}
{ORCA {\normalfont Canoe Tripping Level 3}}
{Gould Lake Outdoor Education Center}
{Trip Leading -- Wilderness leadership and crisis management. \\
Also have certifications in whitewater canoeing and Canadian style paddling.}

%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{work experience}

\begin{entrylist}
%------------------------------------------------

%------------------------------------------------
\entry
{2014}
{Evertz Microsystems}
{Burlington, Ontario}
{\emph{Winter Co\-op}, rated Outstanding \\
Software Developer, Unified Control Systems, Research \& Development. \\
Developed health monitoring system for large scale distributed framework. \\}
%------------------------------------------------
\entry
{2013}
{Babcock \& Wilcox Canada}
{Dundas, Ontario}
{\emph{Summer Co\-op}, rated Excellent \\
Software Developer, Nuclear Services Research \& Development. \\
Researched applications of computer vision in the inspection of nuclear reactors. \\}
%------------------------------------------------
\entry
{2012}
{Toronto Transit Commission}
{Toronto, Ontario}
{\emph{Summer Co\-op}, rated Outstanding \\
Internal IT Service Desk Analyst.}
%------------------------------------------------

%------------------------------------------------
\end{entrylist}

\section{volunteer experience}

\begin{entrylist}
%------------------------------------------------

%------------------------------------------------
\entry
{2012--Present}
{University of Waterloo Fencing Club}
{Waterloo, Ontario}
{\emph{\'{E}p\'{e}e Coach and Armour} \\
Teaching beginner and intermediate lessons. \\}
%------------------------------------------------

%------------------------------------------------
\entry
{2010--2012}
{TVCogeco}
{Kingston, Ontario}
{\emph{Broadcast Crew Member} \\
Mobile production crew, primarily for sports. \\
Live and Live-to-Tape camera work. \\
Live-to-Tape audio mixing.}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------

\section{awards}

\begin{entrylist}
%------------------------------------------------
\entry
{2011}
{Queen Elizabeth II Aiming for the Top Scholarship}
{Ontario}
{Ontario students who have shown academic excellence at the high school level.}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{interests}

Fencing, Interior Camping, Opera Singing and History, Musical Theater, Computer Vision
\end{document}
